High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-05-08 notebooks/circles.qmd
added lin sep

# Benchmark generators:
generator_dict = Dict(
    "Wachter" => WachterGenerator(λ=λ₁),
    "REVISE" => REVISEGenerator(λ=λ₁),
    "Schut" => GreedyGenerator(),
    "ECCCo" => ECCCoGenerator(λ=Λ),
)
```

@@

```{julia}
Random.seed!(2023)

M = model_dict["JEM"]
X = X isa Matrix ? X : Float32.(permutedims(matrix(X)))
factual_label =  levels(labels)[1]
x_factual = reshape(X[:,rand(findall(predict_label(M, counterfactual_data).==factual_label))],input_dim,1)
target =  levels(labels)[2]
factual = predict_label(M, counterfactual_data, x_factual)[1]

@@

bmk = benchmark(
    counterfactual_data; 
    models=model_dict, 
    generators=generator_dict, 
    measure=measures,
    suppress_training=true, dataname="Moons",
    n_individuals=5,
    target=0, factual=1,
    initialization=:identity,
    converge_when=:generator_conditions,
)
CSV.write(joinpath(output_path, "circles_benchmark.csv"), bmk())
```

```{julia}
@chain bmk() begin
    @group_by(dataname, generator, model, variable)
    @summarize(mean=mean(value),sd=std(value))
    @ungroup
    @filter(variable == "distance_from_energy")
end
```

>>>>

# Benchmark generators:
generator_dict = Dict(
    "Wachter" => WachterGenerator(λ=λ₁),
    "REVISE" => REVISEGenerator(λ=λ₁),
    "Schut" => GreedyGenerator(),
    "ECCCo" => ECCCoGenerator(λ=Λ),
    "ECCCo (no CP)" => ECCCoGenerator(λ=[λ₁, 0.0, λ₃]),
    "ECCCo (no EBM)" => ECCCoGenerator(λ=[λ₁, λ₂, 0.0]),
)
```

@@

```{julia}
M = model_dict["JEM"]
X = X isa Matrix ? X : Float32.(permutedims(matrix(X)))
factual_label =  levels(labels)[1]
x_factual = reshape(X[:,rand(findall(predict_label(M, counterfactual_data).==factual_label))],input_dim,1)
target =  levels(labels)[2]
factual = predict_label(M, counterfactual_data, x_factual)[1]

@@

bmks = []
for target in sort(unique(labels))
    for factual in sort(unique(labels))
        if factual == target
            continue
        end
        bmk = benchmark(
            counterfactual_data; 
            models=model_dict, 
            generators=generator_dict, 
            measure=measures,
            suppress_training=true, dataname="Circles",
            n_individuals=5,
            target=target, factual=factual,
            initialization=:identity,
            converge_when=:generator_conditions,
        )
        push!(bmks, bmk)
    end
end
bmk = reduce(vcat, bmks)
CSV.write(joinpath(output_path, "circles_benchmark.csv"), bmk())
```

### 2023-05-08 notebooks/linearly_separable.qmd
added lin sep

# Data:
test_size = 0.2
n_obs = Int(1000 / (1.0 - test_size))
counterfactual_data, test_data = train_test_split(load_circles(n_obs; noise=0.05, factor=0.5); test_size=test_size)
X, y = CounterfactualExplanations.DataPreprocessing.unpack_data(counterfactual_data)
X = table(permutedims(X))
labels = counterfactual_data.output_encoder.labels
input_dim, n_obs = size(counterfactual_data.X)
output_dim = length(unique(labels))
```

@@

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 32
activation = Flux.swish
builder = MLJFlux.MLP(
    hidden=(n_hidden, n_hidden, n_hidden,), 
    σ=activation
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.logitcrossentropy       # loss function
_finaliser = x -> x                         # finaliser function
```

>>>>

# Data:
test_size = 0.2
n_obs = Int(1000 / (1.0 - test_size))
counterfactual_data, test_data = train_test_split(load_linearly_separable(n_obs); test_size=test_size)
X, y = CounterfactualExplanations.DataPreprocessing.unpack_data(counterfactual_data)
X = table(permutedims(X))
labels = counterfactual_data.output_encoder.labels
input_dim, n_obs = size(counterfactual_data.X)
output_dim = length(unique(labels))
```

@@

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 16
activation = Flux.swish
builder = MLJFlux.MLP(
    hidden=(n_hidden, n_hidden, n_hidden,), 
    σ=activation
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.logitcrossentropy       # loss function
_finaliser = x -> x                         # finaliser function
```
